Painting with Triangles

### 2014-04-21 paper.tex
Added paper submission number

\TOGonlineid{45678}
\TOGvolume{0}
\TOGnumber{0}
\TOGarticleDOI{1111111.2222222}
\TOGprojectURL{}
\TOGvideoURL{}
\TOGdataURL{}
\TOGcodeURL{}

@@

\teaser{
  \setlength{\w}{0.33\textwidth}
  \centering
  \includegraphics[width=\w]{images/rainbow3}
  \includegraphics[width=\w]{images/rainbow3_tri}
  \includegraphics[width=\w]{images/rainbow3_zoom3}
  \caption{\emph{Left:} A vector painting made in TrianglePaint exhibits both smooth gradients painted by soft brushes as well as infinitely sharp boundaries painted by hard brushes. \emph{Middle:} The painting is represented by a planar triangle mesh. \emph{Right:} Closeup on the bottom of the letter B highlights both the sharp boundaries on the white region and smooth gradient from blue to green in the background.}
  \label{fig:teaser}
}

@@

In this paper we introduce TrianglePainter which  
uses a different representation than traditional raster or vector graphics.
TrianglePainter uses a triangle mesh to store the data of the painting.
Since triangles are a geometric primitive used in vector graphics this approach achieves the
same advantages traditional vector graphics have. However, the representation allows the
user to paint with vector graphics without dealing directly with the underlying implementation.

@@

To transform a user's mouse inputs to a triangle mesh,
TrianglePainter uses a combination of rasterization and marching squares to
find stroke contours. From the contour it performs a Delaunay triangulation
and then merges this triangulation
of the new stroke with the triangle mesh of the existing canvas. This process yields
a new canvas with the combined strokes.

TrianglePainter reduces the barrier to creating vector graphics by enabling a painting-like interface, with support for sharp and smooth edges. This in turn allows 
artists to focus on the painting and not the way in which they paint, while still 
getting the benefits of vector graphics. We demonstrate our method by creating digital paintings with a 
range of effects and resolutions, including zoom factors of up to 500,000:1 which implies an effective 
resolution equivalent to an image with more than $10^{17}$ pixels.

@@

\subsection{Boundary Edges}
Although the triangles may change over time, they must abide by constraints we call
\emph{boundary edges}, each of which connects a pair of points and specifies that no triangle
can cross it. Like mesh points, boundary edges are persistent. 
%
So as new triangles are created by the triangulation algorithm, they
may never cross a boundary edge.  
This partially restricts the set of valid triangulations of the points.  Figure~\ref{fig:stroke} shows boundary edges for a soft brush stroke.

@@

\section{Discussion and Results}
Paintings made with TrianglePainter can be seen in Figures~\ref{fig:face}, \ref{fig:teaser}, \ref{fig:stop} and \ref{fig:boxes}.  Here we first consider how the complexity of the algorithm grows both in time and geometry.
The results from this analysis and our experience with TrianglePainter have lead to a number of observations.

@@

\begin{figure}
    \centering
        \includegraphics[width=\columnwidth]{images/grid}
    \caption{An example of how TrianglePainter determines which triangles to save and which to retriangulate. Blue
    lines represent the boundaries of old strokes, orange lines are the boundaries of the new stroke, red lines are
    the triangles that will be reused, and purple lines define the area that needs to be retriangulated. The purple
    lines are edges of triangles that intersect the new stroke. Since they interesect the new stroke they are no
    longer valid and must be retriangulated. All other triangles on the canvas can be reused.}
    \label{fig:modified}
\end{figure}

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.195\textwidth]{images/zoom61}
        \includegraphics[width=0.195\textwidth]{images/zoom62}
        \includegraphics[width=0.195\textwidth]{images/zoom63}
        \includegraphics[width=0.195\textwidth]{images/zoom64}
        \includegraphics[width=0.195\textwidth]{images/zoom65}
        \includegraphics[width=0.195\textwidth]{images/zoom66}
        \includegraphics[width=0.195\textwidth]{images/zoom67}
        \includegraphics[width=0.195\textwidth]{images/zoom68}
        \includegraphics[width=0.195\textwidth]{images/zoom69}
        \includegraphics[width=0.195\textwidth]{images/zoom71}
    \caption{A painting that shows extreme zoom levels.  The final image is at zoom level 93,000.}
    \label{fig:boxes}
\end{figure*}

\section{Conclusion}
TrianglePainter enables a user to paint like they would in a raster graphics program 
to create vector graphics. The core of TrianglePainter is a triangle mesh representation of the image.
We have created an algorithm to convert a user's mouse motions into a triangle mesh, and then composite
that mesh on the preexisting mesh containing the previous strokes.

>>>>

\TOGonlineid{33}
\TOGvolume{0}
\TOGnumber{0}
\TOGarticleDOI{1111111.2222222}
\TOGprojectURL{}
\TOGvideoURL{}
\TOGdataURL{}
\TOGcodeURL{}

@@

\teaser{
  \setlength{\w}{0.33\textwidth}
  \centering
  \includegraphics[width=\w]{images/rainbow3}
  \includegraphics[width=\w]{images/rainbow3_tri}
  \includegraphics[width=\w]{images/rainbow3_zoom3}
  \caption{\emph{Left:} A vector painting made in the system exhibits both smooth gradients painted by soft brushes as well as infinitely sharp boundaries painted by hard brushes. \emph{Middle:} The painting is represented by a planar triangle mesh. \emph{Right:} Closeup on the bottom of the letter B highlights both the sharp boundaries on the white region and smooth gradient from blue to green in the background.}
  \label{fig:teaser}
}

@@

In this paper we introduce a system which  
uses a different representation than traditional raster or vector graphics.
The system uses a triangle mesh to store the data of the painting.
Since triangles are a geometric primitive used in vector graphics this approach achieves the
same advantages traditional vector graphics have. However, the representation allows the
user to paint with vector graphics without dealing directly with the underlying implementation.

@@

To transform a user's mouse inputs to a triangle mesh,
the system uses a combination of rasterization and marching squares to
find stroke contours. From the contour it performs a Delaunay triangulation
and then merges this triangulation
of the new stroke with the triangle mesh of the existing canvas. This process yields
a new canvas with the combined strokes.

The system reduces the barrier to creating vector graphics by enabling a painting-like interface, with support for sharp and smooth edges. This in turn allows 
artists to focus on the painting and not the way in which they paint, while still 
getting the benefits of vector graphics. We demonstrate our method by creating digital paintings with a 
range of effects and resolutions, including zoom factors of up to 500,000:1 which implies an effective 
resolution equivalent to an image with more than $10^{17}$ pixels.

@@

\subsection{Boundary Edges}
Although the triangles may change over time, they must abide by constraints we call
\emph{boundary edges}, each of which connects a pair of points and specifies that no triangle
can cross it. Like mesh points, boundary edges are persistent. 
%
So as new triangles are created by the triangulation algorithm, they
may never cross a boundary edge.  
This partially restricts the set of valid triangulations of the points.  Figure~\ref{fig:stroke} shows boundary edges for a soft  stroke.

@@

\section{Discussion and Results}
Paintings made with the system can be seen in Figures~\ref{fig:face}, \ref{fig:teaser}, \ref{fig:stop} and \ref{fig:boxes}.  Here we first consider how the complexity of the algorithm grows both in time and geometry.
The results from this analysis and our experience with the system have lead to a number of observations.

@@

\begin{figure}
    \centering
        \includegraphics[width=\columnwidth]{images/grid}
    \caption{An example of how the system determines which triangles to save and which to retriangulate. Blue
    lines represent the boundaries of old strokes, orange lines are the boundaries of the new stroke, red lines are
    the triangles that will be reused, and purple lines define the area that needs to be retriangulated. The purple
    lines are edges of triangles that intersect the new stroke. Since they interesect the new stroke they are no
    longer valid and must be retriangulated. All other triangles on the canvas can be reused.}
    \label{fig:modified}
\end{figure}

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.195\textwidth]{images/zoom61}
        \includegraphics[width=0.195\textwidth]{images/zoom62}
        \includegraphics[width=0.195\textwidth]{images/zoom63}
        \includegraphics[width=0.195\textwidth]{images/zoom64}
        \includegraphics[width=0.195\textwidth]{images/zoom65}
        \includegraphics[width=0.195\textwidth]{images/zoom66}
        \includegraphics[width=0.195\textwidth]{images/zoom67}
        \includegraphics[width=0.195\textwidth]{images/zoom68}
        \includegraphics[width=0.195\textwidth]{images/zoom69}
        \includegraphics[width=0.195\textwidth]{images/zoom72}
    \caption{A painting that shows extreme zoom levels.  The final image is at zoom level 524,000.}
    \label{fig:boxes}
\end{figure*}

\section{Conclusion}
The system enables a user to paint like they would in a raster graphics program 
to create vector graphics. The core of the system is a triangle mesh representation of the image.
We have created an algorithm to convert a user's mouse motions into a triangle mesh, and then composite
that mesh on the preexisting mesh containing the previous strokes.
